---
title: "Exam 3"
author: "Antonio Tiu"
date: "7/9/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Clear environment
```{r}
rm(list=ls())
```

# 2 Using tidycensus
```{r}
library(tidycensus)


```


# 3. Reshaping inequality_panel wide then using head to peak the data
```{r}
library()
```


# 4. Reshape ineqaulity_wide to long format
```{r}

```


# 5. Showing that inequality_panel and inequality_long have the same data
```{r}

```


# 6. Collapse inequality_long data frame by state
```{r}

```


# 7. Produce map of the U.S that colors in the state polygons by their mean gini scores
```{r}

```


# 8. Use WDI package to import data 
```{r}

```


# 9. Deflate gdp_current to constant 2010 
```{r}

```


# 10. What are the three main components and their subcomponents?
The three main components of Shiny app are the "ui", "server", and "shinyApp". 

# 11. Pull .pdf file
```{r}
library(pdftools)
library(tidyverse)
PDF <- pdf_text("usaid.pdf") %>%
  readr::read_lines()
```


# 12. Convert text pulled from the .pdf to a data frame
```{r}

```


# 13. Tokenize the data by word and remove stop words
```{r}

##mytext=mytext%>%
 # unnest_tokens(word, text)

# get rid of stop words
#data(stop_words)

#mytext <- mytext%>%
 # anti_join(stop_words)

```

# 14. Figure out top 5 most used word 
```{r}
#frequency <- tidy_tweets%>%
 # count(word, sort = TRUE)

#frequency
```


# 15. Load Billboard Hot 100 webpage
```{r}
library(rvest)
library(dplyr)

hot100exam <- "https://www.billboard.com/charts/hot-100"
hot100 <- read_html(hot100exam)
hot100

```


# 16. Use rvest to obtain all of nodes in the webpage
```{r}
body_nodes <- hot100 %>%
  html_node("body") %>%
  html_children()
body_nodes
```



# 17. Using Google Chrome to identify the necessary tags 
```{r}

rank <- hot100 %>% 
  rvest::html_nodes('body') %>%
  xml2:: xml_find_all("//span[contains(@class, 
                      'chart-element__rank__number')]") %>%
  rvest::html_text()

artist <- hot100 %>% 
  rvest::html_nodes('body') %>%
  xml2:: xml_find_all("//span[contains(@class, 
                      'chart-element__information__artist')]") %>%
  rvest::html_text()
  
title <- hot100 %>% 
  rvest::html_nodes('body') %>%
  xml2:: xml_find_all("//span[contains(@class, 
                      'chart-element__information__song')]") %>%
  rvest::html_text()

#last_week <- hot100 %>% 
  #rvest::html_nodes('body') %>%
  #xml2:: xml_find_all("//span[contains(@class, 
           #           'chart-sorter__button font--semi-bold text--center text--uppercase')]") %>%
 # rvest::html_text()

chart_df <- data.frame(rank,artist,title)
```

# Link to Github repo
https://github.com/antoniotiu21/exam3


